---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)

# Import data from published CSV
logged_data <- read_csv(
  "https://docs.google.com/spreadsheets/d/e/2PACX-1vQBv3dyrZKPyzXeenuFfFCxdz_KBLWN2_u59b0KWKxYxXbGnVhIporg96-4mkWql-N0MepXoPHx-98F/pub?gid=2074566949&single=true&output=csv"
)

# Rename variables and clean data
latest_data <- logged_data %>%
  rename(
    ad_type = `What type of product or service is this ad for?`,
    watch_seconds = `How many seconds did I watch the ad for?`,
    known_brand = `Did I already know this brand before seeing the ad?`,
    engagement = `How engaging was the ad?`,
    clicked_ad = `Did I click into the ad?`
  ) %>%
  mutate(
    watch_seconds = as.numeric(watch_seconds),
    engagement = as.numeric(engagement),
    watch_group = case_when(
      watch_seconds <= 5 ~ "0-5 seconds",
      watch_seconds <= 10 ~ "6-10 seconds",
      watch_seconds <= 15 ~ "11-15 seconds",
      TRUE ~ "16+ seconds"
    ),
    watch_group = factor(
      watch_group,
      levels = c("0-5 seconds", "6-10 seconds", "11-15 seconds", "16+ seconds")
    )
  )

# Summary values
mean_watch <- mean(latest_data$watch_seconds, na.rm = TRUE)
mean_engagement <- mean(latest_data$engagement, na.rm = TRUE)
num_ads <- nrow(latest_data)
```

```{css}
body {
  font-family: Arial, sans-serif;
  max-width: 900px;
  margin: 0 auto;
  padding: 20px;
  line-height: 1.6;
  color: #222222;
}

h2 {
  color: #4b2e83;
  border-bottom: 2px solid #4b2e83;
  padding-bottom: 6px;
}

p {
  margin-bottom: 14px;
}
```

## Instagram ads: watch time and engagement

This dynamic report tracks the Instagram ads I observed and focuses on two main questions: how many seconds I watched each ad for, and how engaging I thought the ad was.

So far, I have logged **`r num_ads` ads**. Across these observations, the **average watch time** was **`r round(mean_watch, 1)` seconds**, while the **average engagement rating** was **`r round(mean_engagement, 1)` out of 5**.

These results suggest how long I stayed on an ad and how engaging I found it may be connected. The charts below help show both the overall pattern in watch time and how engagement ratings are distributed across different watch-time groups.

```{r}
ggplot(latest_data, aes(x = watch_group)) +
  geom_bar() +
  labs(
    title = "How Long Instagram Ads Were Watched",
    x = "Watch time group",
    y = "Count"
  )
```

The first chart shows that some ads were watched only briefly, while others held my attention for longer. This gives a simple overview of how long ads usually stayed on my screen.

```{r}
ggplot(latest_data, aes(x = watch_group, fill = factor(engagement))) +
  geom_bar() +
  labs(
    title = "Engagement Ratings Across Watch Time Groups",
    x = "Watch time group",
    y = "Count",
    fill = "Engagement Rating"
  )
```

The second chart compares watch time groups with engagement ratings. If higher engagement ratings appear more often in the longer watch-time groups, that would suggest more engaging ads tended to keep my attention for longer.
